HFI in RISC-V

### 2025-05-01 paper.tex
Updated Paper

\subsection{Implementation - Intial Setup}
Since we were implenting our RISC-V HFI extension in QEMU, we cloned the current open-source QEMU repository and began work there. We began by taking time to understand how QEMU works, the purpose of the various repositories, and gaining a better understanding of RISC-V. We worked with the assumption that the system being run on always supports HFI but it is an easy addition to add any necessary hardware checks to validate that assumption.

>>>>

\subsection{Implementation - Intial Setup}
Since we were implementing our RISC-V HFI extension in QEMU, we cloned the current open-source QEMU repository and began work there. We began by taking time to understand how QEMU works, the purpose of the various repositories, and gaining a better understanding of RISC-V. We worked with the assumption that the system being run on always supports HFI but it is an easy addition to add any necessary hardware checks to validate that assumption.
